Displacement effects and implications of Large-Scale Marine Protected Areas

### 2018-09-14 docs/Manuscript.tex
Updated file

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Displacement effects and implications of Large-Scale Marine Protected Areas},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{natbib}
\bibliographystyle{nature}
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

{
\setcounter{tocdepth}{4}
\tableofcontents
}
\emph{Last update: 2018-09-07}

@@

@@

\caption{\label{tab:unnamed-chunk-3}Mean fishing hours for each gear before and after}
\centering
\begin{tabular}[t]{l|l|r|r|r}
\hline
Gear & Treated & Before & After & Change (A / B)\\
\hline
drifting\_longlines & FALSE & 484.47512 & 470.7382 & 0.9716458\\
\hline
drifting\_longlines & TRUE & 545.68460 & 523.5596 & 0.9594546\\
\hline
purse\_seines & FALSE & 59.64877 & 160.7945 & 2.6956886\\
\hline
purse\_seines & TRUE & 55.30178 & 149.9978 & 2.7123509\\
\hline
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-4}Number of fishing vessels (identified by mmsi) for each gear before and after PIPA implementation.}
\centering
\begin{tabular}[t]{l|l|r|r|r}
\hline
Gear & Treated & Before & After & Change (A / B)\\
\hline
drifting\_longlines & FALSE & 105 & 218 & 2.0761905\\
\hline
drifting\_longlines & TRUE & 139 & 118 & 0.8489209\\
\hline
purse\_seines & FALSE & 49 & 89 & 1.8163265\\
\hline
purse\_seines & TRUE & 78 & 81 & 1.0384615\\
\hline
\end{tabular}
\end{table}

@@

\begin{itemize}
\tightlist
\item
  Divide pipa vessels by type of boat (longline vs.~purse seine)
\item
  Identify two counterfactuals:

  \begin{itemize}
  \tightlist
  \item
    A:

    \begin{itemize}
    \tightlist
    \item
      PNA
    \item
      similar vessel
    \item
      never fished inside PIPA -B:
    \item
      Taiwan
    \item
      Never in PNA
    \item
      Similar region?
    \end{itemize}
  \end{itemize}
\end{itemize}

Has effort increased?

\begin{itemize}
\tightlist
\item
  Change in fishing hours before vs after
\item
  Change in total hours before vs after
\item
  Change in distance before vs after
\item
  Where do PIPA vessels go?
\item
  How many were transient vs local?
\end{itemize}

Has search time increased?

\begin{itemize}
\tightlist
\item
  Distance between fishing points before vs.~after
\item
  Prop hour fishing before vs after
\item
  Time between fishing points before vs.~after
\end{itemize}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-5-1.pdf}
\caption{\label{fig:unnamed-chunk-5}\label{fig:blue_para}Monthly hours,
number of vessels, and data points observed inside PIPA. These clearly
show the blue-paradox effect.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-6-1.pdf}
\caption{\label{fig:unnamed-chunk-6}\label{fig:kir_vessels}Fishing hours and
number of 12 Kiribati vessels from 2012 - 2016 that at some point fished
inside PIPA.}
\end{figure}

\begin{table}[!htbp] \centering 
  \caption{\label{tab:kir_vessels}Fishing hours from GFW for vessels flying Kiribati flag (n = 12). Asterisks indicate significance levels. Numbers in parenthesis represent heteroskedastic-robuste standard errors.} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{hours} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 post & 70.279$^{***}$ & 71.066$^{***}$ & 83.322$^{***}$ & 54.074$^{***}$ \\ 
  & (8.951) & (8.856) & (11.471) & (12.832) \\ 
  & & & & \\ 
 treated & $-$26.777 & $-$27.119 & $-$30.234$^{*}$ & $-$37.149 \\ 
  & (17.881) & (17.137) & (17.434) & (40.248) \\ 
  & & & & \\ 
 post:treated &  &  &  &  \\ 
  &  &  &  &  \\ 
  & & & & \\ 
 Constant & 81.770$^{***}$ & 88.095$^{***}$ & 70.812$^{***}$ & 126.560$^{***}$ \\ 
  & (18.737) & (23.142) & (24.053) & (34.921) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Month FE & No & Yes & Yes & Yes \\ 
Year FE & No & No & Yes & Yes \\ 
Vessel FE & No & No & No & Yes \\ 
Observations & 344 & 344 & 344 & 344 \\ 
R$^{2}$ & 0.170 & 0.191 & 0.219 & 0.383 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-8-1.pdf}
\caption{\label{fig:unnamed-chunk-8}\label{fig:all_vessels}Fishing hours and
number of vessels by month for all vessels that fished inside PIPA at
least once.}
\end{figure}

\begin{table}[!htbp] \centering 
  \caption{\label{tab:all_vessels}Fishing hours from GFW for all vessels (n = 206) that at some point fished in PIPA. Asterisks indicate significance levels. Numbers in parenthesis represent heteroskedastic-robuste standard errors.} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{hours} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 post & 45.766$^{***}$ & 45.268$^{***}$ & 41.959$^{***}$ & 45.596 \\ 
  & (6.534) & (6.504) & (8.779) &  \\ 
  & & & & \\ 
 treated & 50.000$^{***}$ & 51.321$^{***}$ & 50.749$^{***}$ & $-$457.705 \\ 
  & (6.771) & (6.759) & (6.813) &  \\ 
  & & & & \\ 
 postTRUE:treated & $-$59.473$^{***}$ & $-$58.530$^{***}$ & $-$57.494$^{***}$ & $-$21.059 \\ 
  & (8.463) & (8.432) & (8.491) &  \\ 
  & & & & \\ 
 Constant & 349.582$^{***}$ & 328.470$^{***}$ & 333.794$^{***}$ & 483.665 \\ 
  & (5.635) & (8.833) & (10.226) &  \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Month FE & No & Yes & Yes & Yes \\ 
Year FE & No & No & Yes & Yes \\ 
Vessel FE & No & No & No & Yes \\ 
Observations & 15,885 & 15,885 & 15,885 & 15,885 \\ 
R$^{2}$ & 0.004 & 0.011 & 0.011 & 0.632 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-10-1.pdf}

>>>>

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Displacement effects and implications of Large-Scale Marine Protected Areas},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{natbib}
\bibliographystyle{nature}
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\usepackage[normalem]{ulem}
% avoid problems with \sout in headers with hyperref:
\pdfstringdefDisableCommands{\renewcommand{\sout}{}}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

{
\setcounter{tocdepth}{4}
\tableofcontents
}
\emph{Last update: 2018-09-13}

@@

Number of vessels

Explain BACI strict

Analyses being run

Correct number of vessels in tables

Add figure legends

@@

\caption{\label{tab:unnamed-chunk-33}Number of fishing vessels (identified by mmsi) for each gear before and after PIPA implementation.}
\centering
\begin{tabular}[t]{l|l|r|r|r}
\hline
Gear & Treated & Before & After & Change (A / B)\\
\hline
drifting\_longlines & FALSE & 105 & 218 & 2.0761905\\
\hline
drifting\_longlines & TRUE & 139 & 118 & 0.8489209\\
\hline
purse\_seines & FALSE & 49 & 89 & 1.8163265\\
\hline
purse\_seines & TRUE & 78 & 81 & 1.0384615\\
\hline
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-34}Mean fishing hours for each gear before and after}
\centering
\begin{tabular}[t]{l|l|r|r|r}
\hline
Gear & Treated & Before & After & Change (A / B)\\
\hline
drifting\_longlines & FALSE & 481.42502 & 473.5823 & 0.9837094\\
\hline
drifting\_longlines & TRUE & 548.22580 & 524.8121 & 0.9572919\\
\hline
purse\_seines & FALSE & 66.50483 & 172.3775 & 2.5919548\\
\hline
purse\_seines & TRUE & 56.87322 & 146.2015 & 2.5706563\\
\hline
\end{tabular}
\end{table}

@@

\begin{itemize}
\tightlist
\item
  {[}x{]} Divide pipa vessels by type of boat (longline vs.~purse seine)
\item
  {[}x{]} Identify two counterfactuals:

  \begin{itemize}
  \tightlist
  \item
    {[}x{]} A: PNA, similar vessel, never fished inside PIPA
  \item
    {[} {]} B: Taiwan, Never in PNA, Similar region
  \end{itemize}
\item
  {[}x{]} Change in fishing hours before vs after
\item
  {[} {]} \sout{Change in total hours before vs after}
\item
  {[} {]} Change in distance before vs after
\item
  {[} {]} Where do PIPA vessels go?
\end{itemize}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-35-1.pdf}
\caption{\label{fig:unnamed-chunk-35}\label{fig:blue_para}Monthly hours,
number of vessels, and data points observed inside PIPA. These clearly
show the blue-paradox effect.}
\end{figure}

@@

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-36-1.pdf}
\caption{\label{fig:unnamed-chunk-36}\label{fig:all_vessels}Fishing hours
and number of vessels by month for all vessels that fished inside PIPA
at least once.}
\end{figure}

\subsection{Purse seiners}\label{purse-seiners}

\begin{table}[!htbp] \centering 
  \caption{\label{tab:all_vessels}Fishing hours from GFW for all vessels (n = 206) that at some point fished in PIPA. Asterisks indicate significance levels. Numbers in parenthesis represent heteroskedastic-robuste standard errors.} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{hours} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 post & 105.873$^{***}$ & 107.859$^{***}$ & 113.466$^{***}$ & 102.890$^{***}$ \\ 
  & (5.532) & (5.364) & (5.887) & (6.076) \\ 
  & & & & \\ 
 treated & $-$9.632$^{**}$ & $-$8.924$^{**}$ & $-$8.334$^{**}$ & $-$3.076 \\ 
  & (4.257) & (4.023) & (3.725) & (4.540) \\ 
  & & & & \\ 
 post:treated & $-$16.544$^{**}$ & $-$16.889$^{***}$ & $-$17.235$^{***}$ & $-$11.150$^{*}$ \\ 
  & (6.481) & (6.358) & (6.126) & (6.162) \\ 
  & & & & \\ 
 Constant & 66.505$^{***}$ & 61.758$^{***}$ & 40.085$^{***}$ & 61.569$^{***}$ \\ 
  & (3.780) & (5.352) & (5.699) & (9.753) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Month FE & No & Yes & Yes & Yes \\ 
Year FE & No & No & Yes & Yes \\ 
Flag FE & No & No & No & Yes \\ 
Observations & 3,692 & 3,692 & 3,692 & 3,692 \\ 
R$^{2}$ & 0.238 & 0.262 & 0.312 & 0.339 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-37-1.pdf}

\subsection{Longliners}\label{longliners}

\begin{table}[!htbp] \centering 
  \caption{\label{tab:all_vessels}Fishing hours from GFW for all vessels (n = 206) that at some point fished in PIPA. Asterisks indicate significance levels. Numbers in parenthesis represent heteroskedastic-robuste standard errors.} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{hours} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 post & $-$7.843 & $-$4.894 & $-$7.580 & 24.708$^{***}$ \\ 
  & (7.514) & (7.480) & (9.336) & (9.315) \\ 
  & & & & \\ 
 treated & 66.801$^{***}$ & 69.434$^{***}$ & 69.959$^{***}$ & 18.878$^{***}$ \\ 
  & (6.541) & (6.549) & (6.603) & (7.257) \\ 
  & & & & \\ 
 post:treated & $-$15.571$^{*}$ & $-$17.806$^{**}$ & $-$18.340$^{**}$ & $-$25.775$^{***}$ \\ 
  & (8.958) & (8.899) & (8.936) & (8.743) \\ 
  & & & & \\ 
 Constant & 481.425$^{***}$ & 450.475$^{***}$ & 447.866$^{***}$ & 430.947$^{***}$ \\ 
  & (5.733) & (9.239) & (10.280) & (24.476) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Month FE & No & Yes & Yes & Yes \\ 
Year FE & No & No & Yes & Yes \\ 
Flag FE & No & No & No & Yes \\ 
Observations & 8,558 & 8,558 & 8,558 & 8,558 \\ 
R$^{2}$ & 0.026 & 0.044 & 0.044 & 0.107 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-38-1.pdf}
